\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
change order if institutions to match authors, change GNLST to TIB
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64950 15284696-431f-4ddb-bdfa-cd5b030d7da7

\author{
Yann Chemin\inst{2},
V\'{a}clav Petr\'{a}\v{s}\inst{1},
Anna Petr\'{a}\v{s}ov\'{a}\inst{1},
Martin Landa\inst{4},
S\"{o}ren Gebbert\inst{5},
Pietro Zambelli\inst{3},
Markus Neteler\inst{6},
Peter L\"{o}we\inst{7}, and
Margherita Di Leo\inst{8}
}
\institute{
\instlist{1}NCSU, USA;
\instlist{2}IWMI, Sri Lanka;
\instlist{3}EURAC, Italy;
\instlist{4}FCE CTU in Prague, Czech Republic;
\instlist{5}TICSA, Germany;
\instlist{6}CRI, FEM, Italy;
\instlist{7}GNLST, Germany;
\instlist{8}EC-JRC, Italy
}

>>>>

\author{
Yann Chemin\inst{1},
V\'{a}clav Petr\'{a}\v{s}\inst{2},
Anna Petr\'{a}\v{s}ov\'{a}\inst{2},
Martin Landa\inst{3},
S\"{o}ren Gebbert\inst{4},
Pietro Zambelli\inst{5},
Markus Neteler\inst{6},
Peter L\"{o}we\inst{7}, and
Margherita Di Leo\inst{8}
}
\institute{
\instlist{1}IWMI, Sri Lanka;
\instlist{2}NCSU, USA;
\instlist{3}FCE CTU in Prague, Czech Republic;
\instlist{4}TICSA, Germany;
\instlist{5}EURAC, Italy;
\instlist{6}CRI, FEM, Italy;
\instlist{7}TIB Hannover, Germany;
\instlist{8}EC-JRC, Italy
}
